The Hosting Environment of the Advanced Resource Connector middleware

### 2008-08-24 doc/hed/ARCHED_article.tex
A bit about attributes and secattr in HED document

In the current implementation there are no Apache or Axis plugins. That is because the developers of HED were very much concerned about making the solution lightweight and needed an implementation of the supported protocols that was both simple and lightweight. As a result essentials like SOAP and HTTP are implemented inside HED, while external software is used whenever that is found to be appropriate - as in the case of TLS, (Grid)FTP, LDAP and some other cases. ?That does not exclude possibility to have plugins using entirely external solutions either developed or accepted from third parties.?

@@

%As the data is passed through the individual MCCs, they each populate structures with both general attributes and special security attributes that are available at that particular protocol level.

@@

@@

>>>>

In the current implementation there are no Apache or Axis plugins. That is because the developers of HED were very much concerned about making the solution lightweight and needed an implementation of the supported protocols that was both simple and lightweight. As a result essentials like SOAP and HTTP are implemented inside HED, while external software is used whenever that is found to be appropriate - as in the case of TLS, (Grid)FTP, LDAP and some other cases. That does not exclude possibility to have plugins using entirely external solutions either developed or accepted from third parties.?

@@

Each MCC has an entry method which is called with Message being processed. It then processes Message by modifying it or creating new Message. Then MCC calls entry method of next MCC in the chain. For information how mwssages are handled and about memory management policies please see API description of MCC class in [].

As the data is passed through the individual MCCs, they each populate structures with both general attributes and special security attributes that are available at that particular protocol level.

@@

Each MCC developed inside and outside the HED must be accompanied with description of the Payloads it supports on input and those generated on output. Those types should be taken into account while creating chains of the MCCs. There are no Payload type checks done during the chain configuration phase. Hence Payload incompatibility problems will be detected only during runtime.

\paragraph{Attributes}

The Message object may contain general purpose key and value pairs called Attributes. Keys and values are simple stings. Each key may have multiple corresponding values. All pairs are handled by MessageAttributes class. Codewise there are no limitations put on content and purpose of Attributes.

By convention keys are composed of two parts: name of MCC/Protocol at which Attribute was generated or must be consumed and name of Attribute itself separated by column. For example the Attribute with key HTTP:METHOD holds HTTP protocol method like GET, PUT, HEAD, etc. It is either generated MCC implementing HTTP protocol or is filled by other code and is used by HTTP MCC to generate proper HTTP header.

Each MCC developed inside and outside the HED must be have generated and consumed Attributes described in accompanying documentation.

\paragraph{Security Attributes}

Here only basic information about security related objects is presented. For more detailed information please see "Security Framework of ARC1" [].

Security Attributes are storing various aspects of Message useful for authorization decisions to be made. Those normally include operation being requested, target of operation and identity of subject making request. They can also contain authorization policies. Actually nothing stops from storing an other type of information but there is no convention developed for that.

The Secuirity Attributes are stored as key and value pairs. Each key may have only single value attached. Keys are simple strings. By convention each MCC or Security Handler (see below) produce Security Attribute with name corresponding to protocol name. For example Security Attribute stored under name TLS holds information collected at Transport Level Security layer.

The value if Secuirity Attribute is an object of class inherited from SecAttr. The HED implements class SecAttr which serves as definition of interface for all Security Attributes. It defines way collected information may be turned into useful format. For that each Security Attribute value implements method Export for converting internal information into one of supported formats. Currently only implemented is ARC Authorization Request/Policy (see below). Please see API description of SecAttr and MessageAuth classes in [] for more information.

Each MCC developed inside and outside the HED must come with explanation of generated and consumed Security Attributes. Dedicated components for dealing with Security Attribute - Security Handlers are described below.

@@

\paragraph{Client and Server MCCs}
